A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2019-06-20 paper/paper.Rnw
Comment out outline - this is pretty coherent, so I'm not sure we need it in the pdf anymore

\subsection{Model Accuracy}

\mt{\textbf{OUTLINE OF RESULTS}
\begin{itemize}
\item ROC: shows model performance is generally good, gives broad comparison of class performances
\item Examples: show what predictions look like, the model isn't perfect, and motivate that some confusions are systematic between specific classes
\item Confusion Matrix: show patterns in misclassification, motivate diagnostics to explain the cause of common mistakes
\item Two main reasons for error: image contrast, and overlapping features between classes
\begin{itemize}
\item Low contrast: the model can't see features, which affects training and prediction
\item Overlapping features:
\begin{itemize}
\item Many classes share individual features (e.g., lines, angles, curves), so the model already has to integrate features and learn context (e.g., circle vs o)
\item Some classes are also much more variable (see brand plots), which means the model has to widen its definitions of certain shapes, which makes confusion between classes worse
\end{itemize}
\end{itemize}
\item Heatmaps: 1) verify that the model is using category-appropriate features to make decisions and 2) show examples of understandable mistakes
\end{itemize}
}

>>>>

\subsection{Model Accuracy}
%
% \mt{\textbf{OUTLINE OF RESULTS}
% \begin{itemize}
% \item ROC: shows model performance is generally good, gives broad comparison of class performances
% \item Examples: show what predictions look like, the model isn't perfect, and motivate that some confusions are systematic between specific classes
% \item Confusion Matrix: show patterns in misclassification, motivate diagnostics to explain the cause of common mistakes
% \item Two main reasons for error: image contrast, and overlapping features between classes
% \begin{itemize}
% \item Low contrast: the model can't see features, which affects training and prediction
% \item Overlapping features:
% \begin{itemize}
% \item Many classes share individual features (e.g., lines, angles, curves), so the model already has to integrate features and learn context (e.g., circle vs o)
% \item Some classes are also much more variable (see brand plots), which means the model has to widen its definitions of certain shapes, which makes confusion between classes worse
% \end{itemize}
% \end{itemize}
% \item Heatmaps: 1) verify that the model is using category-appropriate features to make decisions and 2) show examples of understandable mistakes
% \end{itemize}
% }
